Elders PM Summary

### 2020-07-24 medvisit_summary.Rmd
data summary updates

```{r, fig.height=3, fig.width=3}
# function for poster plots

fun_data <- elders_medvisit %>% 
  mutate(hypertension = if_else(bp_sys >= 140 | bp_dia >= 90, "Yes", "No"),
         obstruction = if_else(fev1_fvc_ratio < 0.7, "Yes", "No")) %>% 
  select(area, home, home_winter_id, winter_id, sampling_visit, adult_id_num,
         hypertension, obstruction, spiro_status, bp_sys, bp_dia) %>% 
  filter(winter_id == 1) %>% 
  group_by(area, adult_id_num) %>% 
  mutate(hyp_any = if_else(hypertension == "Yes" | lead(hypertension) == "Yes", "Yes", "No"),
         obs_any = if_else(obstruction == "Yes" | lead(obstruction) == "Yes", "Yes", "No")) %>% 
  ungroup() %>% 
  distinct(area, adult_id_num, .keep_all = TRUE) %>% 
  filter(spiro_status == "Acceptable")

@@

medvisit_summary_function(fun_data, "hyp_any", "Stage 2 \nhypertension")
medvisit_summary_function(fun_data, "obs_any", "Obstruction")
```

```{r}
summary_stats <- elders_medvisit %>% 
  filter(winter_id == 1) %>% 
  #filter(spiro_status == "Acceptable") %>% 
  filter(!is.na(bp_sys)) %>% 
  group_by(area) %>% 
  distinct(home) %>% 
  summarize(n())
summary_stats

summary_stats <- elders_medvisit %>% 
  filter(winter_id == 1) %>% 
  filter(!is.na(hypertension)) %>% 
  summarize(sum(hypertension)/n())
summary_stats

summary_stats <- elders_medvisit %>% 
  filter(winter_id == 1) %>% 
  filter(spiro_status == "Acceptable") %>% 
  filter(!is.na(obstruction)) %>% 
  summarize(sum(obstruction)/n())
summary_stats
```

>>>>

```{r, fig.height=3, fig.width=3}
# poster figures
obstruction_data <- elders_medvisit %>% 
  arrange(home, adult_id_num, winter_id, sampling_visit) %>% 
  mutate(hypertension = if_else(bp_sys >= 140 | bp_dia >= 90, "Yes", "No"),
         obstruction = if_else(fev1_fvc_ratio < 0.7, "Yes", "No")) %>% 
  select(area, home, home_winter_id, winter_id, sampling_visit, adult_id_num,
         hypertension, obstruction, spiro_status, bp_sys, bp_dia) %>%
  filter(winter_id == 1) %>% 
  filter(spiro_status == "Acceptable") %>% 
  group_by(area, adult_id_num) %>% 
  mutate(obs_any = if_else(obstruction == "Yes" | lead(obstruction) == "Yes", "Yes", "No"),
         obs_any = if_else(is.na(obs_any), obstruction, obs_any)) %>% 
  ungroup() %>% 
  distinct(area, adult_id_num, .keep_all = TRUE) %>% 
  count(obs_any)
obstruction_data

hypertension_data <- elders_medvisit %>% 
  arrange(home, adult_id_num, winter_id, sampling_visit) %>% 
  mutate(hypertension = if_else(bp_sys >= 140 | bp_dia >= 90, "Yes", "No"),
         obstruction = if_else(fev1_fvc_ratio < 0.7, "Yes", "No")) %>% 
  select(area, home, home_winter_id, winter_id, sampling_visit, adult_id_num,
         hypertension, obstruction, spiro_status, bp_sys, bp_dia) %>%
  filter(winter_id == 1) %>% 
  group_by(area, adult_id_num) %>% 
  mutate(hyp_any = if_else(hypertension == "Yes" | lead(hypertension) == "Yes", "Yes", "No"),
         hyp_any = if_else(is.na(hyp_any), hypertension, hyp_any)) %>% 
  ungroup() %>% 
  distinct(area, adult_id_num, .keep_all = TRUE) %>% 
  count(hyp_any)
hypertension_data

@@

medvisit_summary_function(hypertension_data, "hyp_any", "Stage 2 \nhypertension")
medvisit_summary_function(obstruction_data, "obs_any", "FEV1/FVC ratio \n< 0.7")
```

```{r}
summary_stats <- elders_medvisit %>% 
  filter(winter_id == 1) %>% 
  #filter(spiro_status == "Acceptable") %>% 
  #filter(!is.na(bp_sys)) %>% 
  #group_by(area) %>% 
  distinct(area, adult_id_num) %>% # use home and adult_id_num
  summarize(n())
summary_stats

summary_stats <- elders_medvisit %>% 
  filter(winter_id == 1) %>% 
  distinct(area, adult_id_num, .keep_all = TRUE) %>% 
  #group_by(area) %>% 
  count(gender)
summary_stats

summary_stats <- elders_medvisit %>% 
  filter(winter_id == 1) %>% 
  distinct(area, adult_id_num, .keep_all = TRUE) %>% 
  #group_by(area) %>% 
  summarize(mean(bmi, na.rm = TRUE), sd(bmi, na.rm = TRUE), 
            min(bmi, na.rm = TRUE), median(bmi, na.rm = TRUE), 
            max(bmi, na.rm = TRUE))
summary_stats
```

### 2020-07-24 pm_summary_dustrak.Rmd
data summary updates

>>>>

\pagebreak

```{r, fig.height=4, fig.width=4}
boxplots_elders_pm <- elders_pm %>% 
  filter(winter_id == 1) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  ungroup() %>% 
  ggplot(aes(area, pm_mean)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=4, color="red") +
    #scale_y_log10() +
    ylim(0, 200) +
    theme_minimal() +
    labs(y = expression(paste("PM"[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black",
                                      margin = margin(t = 0, r = 0, b = 30, l = 0)),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_elders_pm

ggsave("boxplots_elders_pm.jpg", height = 7, width = 4)
```

```{r}
# homes that exceed PM guidelines
pm_guidelines <- elders_pm %>% 
  filter(winter_id == 1) %>% 
  group_by(home) %>% 
  mutate(pm_mean_winter = mean(pm_mean, na.rm = TRUE)) %>% 
  filter(pm_mean_winter > 35) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  group_by(area) %>% 
  count()
pm_guidelines
```
